Probabilistic Catalogs from Crowded Star Fields

### 2012-10-04 paper/ms.tex
the rest of the comments

\subsection{The Sampling Distribution}
The sampling distribution is a probabilistic model for the process that
generates the data; it describes the probability distribution we would use
to predict the data if we happened to know the true catalog. In our case,
the data will be an $n \times n$ {\bf (we're already using $N$ for the
number of stars\ldots it might be better to use a different letter here.}
array of pixel intensities:
\begin{eqnarray}
\{Y_{ij}\}
\end{eqnarray}
The center of each pixel is:
\begin{eqnarray}
    \{x_{ij}, y_{ij}\}. \quad \mathrm{couldn't~this~be}\,\{x_i, y_j\}?
\end{eqnarray}
{\bf I also find the notation a little confusing here\ldots I think that we
need different variables for the star positions and the pixel coordinates.}
Thus, we need
a prescription for simulating an image $\{Y_{ij}\}$ from a catalog $\theta$:
\begin{eqnarray}
\theta = \left\{N, \beta, \left\{x_i, y_i\right\}_{i=1}^N,
\left\{f_i\right\}_{i=1}^N\right\}.
\end{eqnarray}
If we knew the true catalog, we could compute the
``mock image'' we would expect to see
in the absence of noise. This mock image (at infinite resolution) is given by:
\begin{eqnarray}
\mathcal{M}(x, y) &=& \sum_{i=1}^N \mathcal{P}(x - x_i, y - y_i)
\end{eqnarray}
where $\mathcal{P}$ is the pixel-convolved point spread function (PSF).
Throughout this paper we
assume the pixel-convolved PSF is a known weighted mixture of two concentric
circular
Gaussians with widths $s_1$ and $s_2$:
\begin{eqnarray}
\mathcal{P}(x, y) = \frac{w}{2\pi s_1^2}\exp
\left[
-\frac{1}{2s_1^2}\left(x^2 + y^2\right)
\right]
+ \frac{1-w}{2\pi s_2^2}\exp
\left[-\frac{1}{2s_2^2}\left(x^2 + y^2\right)
\right].
\end{eqnarray}
The finite-resolution observed image is assumed to be generated from the mock
image (evaluated at the center of each pixel) plus Gaussian noise:
\begin{eqnarray}
Y_{ij} &=& \mathcal{M}(x_{ij}, y_{ij}) + \epsilon_{ij}
\end{eqnarray}
where the errors $\{\epsilon_{ij}\}$ are independent and normally distributed:
\begin{eqnarray}
\epsilon_{ij} \sim \mathcal{N}(0, \sigma^2).
\end{eqnarray}
Throughout this paper, we will assume that the noise variance $\sigma^2$ is
known. This is not usually true in practice (although it is often assumed).
However it is straightforward to extend the model so that $\sigma$ is an
unknown parameter or that the noise variance should be a function of the
intensity of the mock image \citep[e.g.][]{2011MNRAS.412.2521B}.

@@

\section{Broken Power-Law Distribution}\label{power_law}
The broken power-law distribution is based on a straightforward extension
to a simple power-law distribution (also known as a Pareto distribution,
particularly in the statistics literature).
The broken power-law distribution for a variable $x$ is defined by:
\begin{eqnarray}
p(x) &\propto&
\left\{
\begin{array}{lcr}
0, & & x < x_1 \\
x^{-\alpha_1 - 1} & & x_1 \leq x \leq x_2 \\
x^{-\alpha_2 - 1} & & x > x_2
\end{array}
\right.
.
\end{eqnarray}
The free parameters of the broken power-law are:
\begin{eqnarray}
\beta = \{x_1, x_2, \alpha_1, \alpha_2\}
\end{eqnarray}

>>>>

\subsection{The Sampling Distribution}
The sampling distribution is a probabilistic model for the process that
generates the data; it describes the probability distribution we would use
to predict the data if we happened to know the true catalog. In our case,
the data will be an $n \times n$ {\bf (we're already using $N$ for the
number of stars\ldots it might be better to use a different letter here.}
array of pixel intensities:
\begin{eqnarray}
\{Y_{ij}\}
\end{eqnarray}
The center of each pixel is:
\begin{eqnarray}
    \{x_{ij}, y_{ij}\}. \quad \mathrm{couldn't~this~be}\,\{x_i, y_j\}?
\end{eqnarray}
{\bf I also find the notation a little confusing here\ldots I think that we
need different variables for the star positions and the pixel coordinates.}
Thus, we need
a prescription for simulating an image $\{Y_{ij}\}$ from a catalog $\theta$:
\begin{eqnarray}
\theta = \left\{N, \beta, \left\{x_i, y_i\right\}_{i=1}^N,
\left\{f_i\right\}_{i=1}^N\right\}.
\end{eqnarray}
If we knew the true catalog, we could compute the
``mock image'' we would expect to see
in the absence of noise. This mock image (at infinite resolution)
{\bf $\gets$ Hogg already mentioned this, but I wanted to reiterate that
this doesn't seem like the word you want here\ldots}
is given by:
\begin{eqnarray}
\mathcal{M}(x, y) &=& \sum_{i=1}^N \mathcal{P}(x - x_i, y - y_i)
\end{eqnarray}
where $\mathcal{P}$ is the pixel-convolved point spread function (PSF).
Throughout this paper we
assume the pixel-convolved PSF is a known weighted mixture of two concentric
circular
Gaussians with widths $s_1$ and $s_2$:
\begin{eqnarray}
\mathcal{P}(x, y) = \frac{w}{2\pi s_1^2}\exp
\left[
-\frac{1}{2s_1^2}\left(x^2 + y^2\right)
\right]
+ \frac{1-w}{2\pi s_2^2}\exp
\left[-\frac{1}{2s_2^2}\left(x^2 + y^2\right)
\right].
\end{eqnarray}
The finite-resolution observed image is assumed to be generated from the mock
image (evaluated at the center of each pixel) plus Gaussian noise:
\begin{eqnarray}
Y_{ij} &=& \mathcal{M}(x_{ij}, y_{ij}) + \epsilon_{ij}
\end{eqnarray}
where the errors $\{\epsilon_{ij}\}$ are independent and normally distributed:
\begin{eqnarray}
\epsilon_{ij} \sim \mathcal{N}(0, \sigma^2).
\end{eqnarray}
Throughout this paper, we will assume that the noise variance $\sigma^2$ is
known. This is not usually true in practice (although it is often assumed).
However it is straightforward to extend the model so that $\sigma$ is an
unknown parameter or that the noise variance should be a function of the
intensity of the mock image \citep[e.g.][]{2011MNRAS.412.2521B}.

@@

\section{Broken Power-Law Distribution}\label{power_law}

{\bf I love this\ldots Good addition!}

The broken power-law distribution is based on a straightforward extension
to a simple power-law distribution (also known as a Pareto distribution,
particularly in the statistics literature).
The broken power-law distribution for a variable $x$ is defined by:
\begin{eqnarray}
p(x) &\propto&
\left\{
\begin{array}{lcr}
0, & & x < x_1 \\
x^{-\alpha_1 - 1} & & x_1 \leq x \leq x_2 \\
x^{-\alpha_2 - 1} & & x > x_2
\end{array}
\right.
.
\end{eqnarray}
The free parameters of the broken power-law are:
\begin{eqnarray}
\beta = \{x_1, x_2, \alpha_1, \alpha_2\}
\end{eqnarray}
